Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-06 hybrid_placement.tex
remove TODO in Section 6

\TODO{Is this reasonable?}

@@

\TODO{How's this?}
These initial experiments demonstrate some degree of benefit derived from using a hybrid approach, helping to alleviate the ``bully'' effect while retaining the performance of communication-intensive applications. However, the behavior is still not ideal in this case -- AMG's communications still experience performance degradation versus the contiguous configurations. Hence, more work in this area is needed to fully understand the intricate relationships between job scheduling and system/application communication behavior to approach optimal network utilization and application performance in high-radix networks.

>>>>

%\TODO{Is this reasonable? So much better}

@@

%\TODO{How's this? Awesome}
These initial experiments demonstrate some degree of benefit derived from using a hybrid approach, helping to alleviate the ``bully'' effect while retaining the performance of communication-intensive applications. However, the behavior is still not ideal in this case -- AMG's communications still experience performance degradation versus the contiguous configurations. Hence, more work in this area is needed to fully understand the intricate relationships between job scheduling and system/application communication behavior to approach optimal network utilization and application performance in high-radix networks.
